### 2019-12-06 reports/media/loosely_acc.tex
remove second accelerator

  \node (hwacc1) at (3,0.2) [hwacc] {ACC};
  \begin{scope}[name=completeacc, local bounding box=accbb, shift={(3, 0.2)}]
    \node (reg0) [accint, minimum width=25pt, xshift=-5pt, minimum height=5pt, font=\tiny] {REG 0};
    \node (reg1) [accint, minimum width=25pt, minimum height=5pt, below=of reg0, font=\tiny] {REG 1};
    \node (reg2) [accint, minimum width=25pt, minimum height=5pt, below=of reg1, font=\tiny] {REG N};
    \node (spm) [accint, minimum height=15pt, minimum width=5pt, align=center,
    right=of reg0.north east, font=\tiny, anchor=north west] {S\\P\\M};
    \node (accpe) [accint, minimum width=10pt, minimum height=10pt, above=of reg0.north west,
    anchor=south west, font=\tiny] {PE};
    \node (accctl) [accint, minimum width=10pt, minimum height=10pt, above=of spm.north east,
    anchor=south east, font=\tiny] {CTL};
  \end{scope}

  \node (hwacc2) at (5,0.2) [hwacc] {ACC};

  \node (mainbus) at (-1, -2) [bus, anchor=west, minimum height=200pt] {};

  \node at (core0.south) [bus, rotate=90, anchor=east, scale=0.5, minimum height=57pt] {};
  \node at (hwacc1.south) [bus, rotate=90, anchor=east, scale=0.5, minimum height=68pt] {};
  \node at (hwacc2.south) [bus, rotate=90, anchor=east, scale=0.5, minimum height=68pt] {};

  \node (gpc) [fit=(core0)(core1)(core2), rounded corners,
  dashed, draw, minimum height=60pt, label={[align=center]90:{General\\ purpose}}] {};
  \node (dsc) [fit=(hwacc1)(hwacc2), rounded corners, dashed,
  draw, minimum height=60pt, label={[align=center]90:{Domain\\ specific}}] {};

  \draw[-latex] (hwacc1.west) -- ++(-1,0) node [anchor=south west] {\tiny int};
  \draw[-latex] (hwacc2.west) -- ++(-0.25, 0) -- ++(0, 0.9) -- ++(-2.75, 0) node [anchor=south west] {\tiny int};
  \end{scope}

@@

  \node [fit=(socbb), draw, dashed, rounded corners, thick, inner sep=6pt, label={320:SoC}] {};

>>>>

  \node (hwacc1) at (3,0.2) [hwacc] {ACC};
  \begin{scope}[name=completeacc, local bounding box=accbb, shift={(3, 0.2)}]
    \node (reg0) [accint, minimum width=25pt, xshift=-5pt, minimum height=5pt, font=\tiny] {REG 0};
    \node (reg1) [accint, minimum width=25pt, minimum height=5pt, below=of reg0, font=\tiny] {REG 1};
    \node (reg2) [accint, minimum width=25pt, minimum height=5pt, below=of reg1, font=\tiny] {REG N};
    \node (spm) [accint, minimum height=15pt, minimum width=5pt, align=center,
    right=of reg0.north east, font=\tiny, anchor=north west] {S\\P\\M};
    \node (accpe) [accint, minimum width=10pt, minimum height=10pt, above=of reg0.north west,
    anchor=south west, font=\tiny] {PE};
    \node (accctl) [accint, minimum width=10pt, minimum height=10pt, above=of spm.north east,
    anchor=south east, font=\tiny] {CTL};
  \end{scope}
  \node (mainbus) at (-1, -2) [bus, anchor=west, minimum height=140pt] {};

  \node at (core0.south) [bus, rotate=90, anchor=east, scale=0.5, minimum height=57pt] {};
  \node at (hwacc1.south) [bus, rotate=90, anchor=east, scale=0.5, minimum height=68pt] {};

  \node (gpc) [fit=(core0)(core1)(core2), rounded corners,
  dashed, draw, minimum height=60pt, label={[align=center]90:{General\\ purpose}}] {};
  \node (dsc) [fit=(hwacc1), rounded corners, dashed, inner sep=10pt,
  draw, minimum height=60pt, label={[align=center]90:{Domain\\ specific}}] {};

  \draw[-latex] (hwacc1.west) -- ++(-1,0) node [anchor=south west] {\tiny int};
  \end{scope}

@@

  \node [fit=(socbb), draw, dashed, rounded corners, thick, inner sep=6pt, label={300:SoC}] {};
